Probability

### 2016-04-18 prob.tex
Start adding comments...

A classical model decides the occurrence or non-occurence of all
events simultaneously which is inconsistent with quantum
mechanics. Indeed, in the quantum world, there are (non-commuting)
events which cannot happen simultaneously. To accommodate this
situation, we completely abandon the sample space $\Omega$ and define
and reason directly about events. Thus a quantum probability space
will consist of just two components: a set of events $\qevents$ and a
probability measure $\phi : \qevents \rightarrow [0,1]$. These
components are defined as follows.

We first assume an ambient Hilbert space $\Hilb$ and define the set of
events $\qevents$ as \emph{projections} on $\Hilb$. Similarly to the
classical case, a probability measure is a function
$\phi : \qevents \rightarrow [0,1]$ satisfying:
\begin{itemize}
\item $\phi(\mathbbm{1}) = 1$, and
\item for all $A \in \qevents$, we have $\phi(A^*A) \geq 0$.
\end{itemize}

As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
Each state $\ket{\psi}$ of the Hilbert space induces a probability
measure $\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \ip{\psi}{A\psi}
\]

%% If we want to follow Swart~\cite{Swart2013} 
%% I am following sec 4 of https://www.math.ru.nl/~maassen/lectures/Trieste.pdf

>>>>

A classical model decides the occurrence or non-occurence of all
events simultaneously which is inconsistent with quantum
mechanics. Indeed, in the quantum world, there are (non-commuting)
events which cannot happen simultaneously. To accommodate this
situation, we completely abandon the sample space $\Omega$ and define
and reason directly about events. Thus a quantum probability space
will consist of just two components: a set of events $\qevents$ and a
probability measure $\phi : \qevents \rightarrow [0,1]$. These
components are defined as follows~\cite{Maassen2010,Swart2013}.

We first assume an ambient Hilbert space $\Hilb$ and define the set of
events $\qevents$ as \emph{projections} on $\Hilb$. Similarly to the
classical case, a probability measure is a function
$\phi : \qevents \rightarrow [0,1]$ satisfying:
\begin{itemize}
\item $\phi(\mathbbm{1}) = 1$, and
\item for all $A \in \qevents$, we have $\phi(A^*A) \geq 0$.
\end{itemize}
\yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
need 
\begin{itemize}
\item $\phi$ can be extended to a linear functional~$\phi:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
by $\qevents$.
\end{itemize}
}\\
As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
\yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
can generate (and something more) not just projections. For example,
$2\mathbbm{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\
Each state $\ket{\psi}$ of the Hilbert space induces a probability
measure $\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \ip{\psi}{A\psi}
\]
\yutsung{So $\phi_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{i},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
to $\mathbb{C}$...}\\
